Road Segment Prioritization for Bicycle Infrastructure

### 2021-03-06 README.Rmd
Update final section, new reference

It should be noted that the calculations assume cycling in the
traditional sense, i.e. the topography affects the decision to cycle.
Recently there have been various micro-mobility solutions, including
e-bikes, that allow commuters to traverse longer distances and hillier
roads with less effort than traditional bicycles. While these modes
would probably be associated with less geographical impedance, it is
beyond the scope of this work to integrate those modes into the
analysis. This is partially restricted by the lack of data on the
proliferation of these modes, raising the point that perhaps the census
data category of `Bicycle' is too vague, and should be further
disaggregated to distinguish between traditional bicycles and other
forms of micro-mobility.

@@

This paper provides a methodology for prioritizing road segments for
investments in cycling infrastructure, with the output being a proposed
cycling network for the city under study. The approach aims to respect
both the needs of the users and the ambitions of stakeholders working at
local or regional levels. The results, primarily detailed route network
maps based on current travel behaviour derived from OD data, can provide
an evidence-based starting point for introducing a direct, connected,
and low-stress network for any city by leveraging available open data.
Given that the "most essential activity entailed in the design of
cycle-friendly infrastructure is developing a cycle network"
[@parkin2018designing], we believe that the methods have great
potential to inform investment in cities such as Manchester where there
is political will to invest in cycling long-term. A benefit of the
approach is that it has relatively modest data requirements: only the
road network (from OSM), its topography (from satellite imagery), and
OD data (from the national census in this case) are
needed, opening up the possibility of deploying the approach in other
cities^[The results are easily reproducible for all UK cities, and can
also be reproduced for cities elsewhere given the availability of
commuter data. For instructions on reproducing the results shown in this
paper, see the **README** file in the R folder of the .zip file that
accompanies this paper (to be released as open source software when the
paper is published).].

@@

A core part of the methodology is determining where there is a high
potential for cycling, and using this as a basis for recommendations on
road space reallocation in order to unlock potential cycling demand. The
framework provides a routing engine to study the effects of limiting
access on different road types, finding that reducing cyclist flow on
roads with high through-traffic results in acceptable increases in
commuting distances. As a result, a hierarchy of road preference needs
to be defined to route potential cycling demand. The framework provides
an algorithm to determine where investments in cycling
infrastructure should be prioritized. This algorithm, based on
connectivity and egalitarian principles of resource distribution,
ensured that whatever the level of investment, the resulting cycling
network would improve connectivity of existing cycling infrastructure.
The algorithm was also shown to provide similar city-wide results as well better distribution of investment when compared to one based on utilitarian principles.

>>>>

The uptake model used in this paper assumes uptake of traditional bicycles,
which are affected by topography and distance due to physical effort.
As discussed in Section \@ref(discussion-and-conclusions), using adapted uptake
models could enable the approach to help plan for solutions such as e-bikes
that enable trips covering longer distances and hillier roads.

@@

This paper demonstrates an approach for prioritizing
investments in city-wide cycleway networks. The approach aims to respect
both the needs of the users and the ambitions of stakeholders working at
local or regional levels. The results, including detailed route network
maps based on current travel behaviour derived from OD data, can provide
an evidence-base for designing direct, connected,
and low-stress networks.

Given that the "most essential activity entailed in the design of
cycle-friendly infrastructure is developing a cycle network"
[@parkin2018designing], we believe that the methods have great
potential to inform investment in cities such as Manchester where there
is political will to invest in cycling long-term. A benefit of the
approach is that it has relatively modest data requirements: only the
road network (from OSM), its topography (from satellite imagery), and
OD data (from the national census in this case) are
needed, opening up the possibility of deploying the approach in other
cities^[The results are easily reproducible for all UK cities, and can
also be reproduced for cities elsewhere given the availability of
commuter data. For instructions on reproducing the results shown in this
paper, see the **README** file in the R folder of the .zip file that
accompanies this paper (to be released as open source software when the
paper is published).].

@@

The approach can identify not only where there is high
potential for cycling but also trade-offs between
quietness (the absence of motor traffic) and directness.
The results can therefore be used as a basis for recommendations on
road space reallocation *and* new infrastructure to unlock potential cycling demand.
The approach encourages consideration of a wider range of preferences
and needs that previous methods that focus only on absolute potential.
Moreover, the inclusion of egalitarian principles in scenarios of change
encourages investment in cycling infrastructure to
increase the connectivity of existing cycling infrastructure
*and* investment that addresses geographical and social inequalities.
This ability to address inequalities in network prioritisation is particularly
important given research research showing substantial *inequalities*
around transport provision in general and cycling uptake and investment
in particular [@lucas2016method; @vidaltortosa_infrastructure_2020].
